BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-11-29 tex/3-algorithms.tex
Re-read all the paper, lots of rephrasing.

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation}
% html extraction is not trival
Extracting metadata and content from HTML documents is a challenging task. Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organized. For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}. More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantic information and metadata inside HTML documents, but still suffer from very low usage: under 0.5\%\cite{andrewrogers2013}. In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organize structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}. Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques have to be employed.

@@

% assumptions when working with blogs
Having blogs as our target websites we made the following assumptions that play a central role in the extraction process\Anote{assumptions}:
\begin{enumerate}[label={(\arabic*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the most recent posts of a blog,\TODO{mention RSS and Atom, just to confirm to the reader what a web feed is?}
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
\end{enumerate}
Web feeds usually contain about 20 posts\cite{oita2010}, often less than the total number of posts in blogs. Consequently, in order to effectively archive old content from blogs it is necessary to download and process pages beyond the ones referenced in the feed.

@@

% algorithm, inputs/output
Algorithm \ref{extractionAlgo} shows the steps we follow to build extraction rules for the content pof blog posts. As input, it takes a set of pairs of HTML pages and target contents, and finally returns an extraction rule. This rule is such that when applied to other input pages, the extracted contents are as similar as possible to the corresponding target contents.

% general idea, embarrassingly parallel
The idea is quite simple: to compute the best extraction rule for each pair of HTML page and target conent and to finally return the most frequent best rule. Making each of these computations independent might seem like a loss of information compared to alternative solutions such as having a global score for each rule, computed as the average of each rule's score over all the pages of the feed. In our experimentation we observed several cases where the independent solution performs better\TODO{example, reference or proof?}. When web feeds have many posts with very short content each, mean based solutions tend to be more influenced by these outliers and are inclined to return erronous rules which fail to return target contents but constantly have an average score.

In addition, having a independent computation for each input makes the algorithm \emph{embarrassingly parallel}\comment{it's a coined term, so it's fine, but should we have a reference here? -> Can't find a good one..}: iterations of the outer loop can trivialy be executed by multiple threads.

% input from assumptions.
Before going into further details about annex functions and time complexity, we should explain how the previously stated assumptions relate to Algorithm \ref{extractionAlgo}. Given a blog, assumption \ref{havefeedAssum} allows the crawler to obtain input for the algorithm. Indeed, web feeds provide either textual content or descriptions for their entries, as well as links to the corresponding pages. Assumption \ref{similarhtmlAssum} guaranties the existence of an appropriate an extraction rule, as well as its applicability to all the posts of a blog.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction rules and string similarity}
% xpath selectors (id, else class, else path)
In our implementation, rules are queries in the XML Path Language (XPath). Consequently, standard libraries can be used parse HTML pages and apply extraction rules, thus providing the \code{Apply} function, used in Algorithm \ref{extractionAlgo}. We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absolute path in the HTML tree. \code{id} attributes are expected to be unique, and \code{class} attributes have showed to have better blog consistency than absolute paths. For these reasons, the \coderef{allrulesAlgo} function only returns the best rule for each node:

@@

% Linear reformulation
We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time. While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from an effective reuse of previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string. To overcome this limitation and implement $memoization$ \comment{without R!}over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams. This way we avoid serializing HTML subtrees for each bigram computation and we can guarantee that each character of the HTML page will be read at most once during the bigrams computation. Thus, the cumlated time needed to compute bigrams of \emph{node.text} is linear.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Variations for authors, dates and comments}
% Intro
In the current state algorithms \ref{extractionAlgo} and \ref{linearAlgo} will performe poorly for author and date extraction and are not suitable for comment extraction. This subsection presents variations on the general extraction techniques presented before. Due to space constraints, we will only provide the main ideas and omit algorithmic and implementation details.

% Authors
The case of authors is problematic because it is not uncommon to encounter the author's name at several places in a page, leading to several rules with maximum score. The heuristic we use to get around this issue consists of adding a new component in the scores of authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node. This new score component takes advantage of the positioning of post's authors which is often a direct child or shares parent with the post content node.

@@

% Comments
Comments are usually available in separate web feeds, one per blog post. Similarly to blog feeds, comment feeds have a limited number of entries, and in case a blog post has more comments than the ones appearing in the feed, comments have to be extracted from the post web page. To do so we use algorithm \ref{extractionAlgo} with the following modifications:
\begin{enumerate}
  \item\label{lessthanfeedMod} Rules that return less HTML nodes than the number of comments on the feed are filtered out.
  \item\label{assignmentMod} The score of a rule is the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
\end{enumerate}
Our crawler executes this algorithm on each post that present a comment feed overflow, thus supporting blogs with multiple commenting engines. Comment contents are extracted first, which allows to narrow down modifications \ref{lessthanfeedMod} by fixing the target number of comments.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation}
% html extraction is not trival
Extracting metadata and content from HTML documents is a challenging task. Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organized. For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}. More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantic information and metadata inside HTML documents, but still suffer from very low usage: under 0.5\%\cite{andrewrogers2013}. In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organize structure pages\cite{brianwilson2008}\TODO{FIX REF!}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}. Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques have to be employed.

@@

% assumptions when working with blogs
Having blogs as our target websites we made the following assumptions that play a central role in the extraction process\Anote{assumptions}:
\begin{enumerate}[label={(\arabic*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the most recent posts of a blog,\TODO{mention RSS and Atom, just to confirm to the reader what a web feed is?}
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
\end{enumerate}
Web feeds usually contain about 20 posts\cite{oita2010}, often less than the total number of posts in blogs. Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in the feed.

@@

% algorithm, inputs/output
Algorithm \ref{extractionAlgo} shows the steps we follow to build extraction rules for the content of blog posts. As input, it takes a set of pairs of HTML pages and target contents, and finally returns an extraction rule. This rule is such that when applied to other input pages, the extracted contents are as similar as possible to the corresponding target contents.

% general idea, embarrassingly parallel
The idea is quite simple: to compute the best extraction rule for each pair of HTML page and target content and to finally return the most frequent best rule. Making each of these computations independent might seem like a loss of information compared to alternative solutions such as having a global score for each rule, computed as the average of each rule's score over all the pages of the feed. In our experimentation we observed several cases where the independent solution performs better\TODO{example, reference or proof?}. When web feeds have posts with very short content, mean based solutions tend to be more influenced by these outliers and are inclined to return erronous rules which fail to return target contents but constantly have an average score.\TODO{rephrase!}

In addition, having an independent computation for each input makes the algorithm \emph{embarrassingly parallel}\comment{it's a coined term, so it's fine, but should we have a reference here? -> Can't find a good one..}: iterations of the outer loop can trivialy be executed by multiple threads.

% input from assumptions.
Before going into further details about annex functions and time complexity, we should explain how the previously stated assumptions relate to Algorithm \ref{extractionAlgo}. Given a blog, assumption \ref{havefeedAssum} allows the crawler to obtain input for the algorithm. Indeed, web feeds provide either textual content or descriptions for their entries, as well as links to the corresponding pages. Assumption \ref{similarhtmlAssum} guaranties the existence of an appropriate extraction rule, as well as its applicability to all the posts of a blog.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction rules and string similarity}
% xpath selectors (id, else class, else path)
In our implementation, rules are queries in the XML Path Language (XPath). Consequently, standard libraries can be used to parse HTML pages and apply extraction rules, thus providing the \code{Apply} function, used in Algorithm \ref{extractionAlgo}. We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absolute path in the HTML tree. \code{id} attributes are expected to be unique, and \code{class} attributes have showed to have better blog consistency than absolute paths. For these reasons, the \coderef{allrulesAlgo} function only returns the best rule for each node:

@@

% Linear reformulation
We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time. While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from an effective reuse of previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string. To overcome this limitation and implement $memoization$ \comment{without R!}over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams. This way we avoid serializing HTML subtrees for each bigram computation and we can guarantee that each character of the HTML page will be read at most once during the bigrams computation. Thus, the cumulated time needed to compute bigrams of \emph{node.text} is linear.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Variations for authors, dates and comments}
% Intro
In the current state algorithms \ref{extractionAlgo} and \ref{linearAlgo} will perform poorly for author and date extraction and are not suitable for comment extraction. This subsection presents variations on the general extraction techniques presented before. Due to space constraints, we will only provide the main ideas and omit algorithmic and implementation details.

% Authors
The case of authors is problematic because it is not uncommon to encounter the author's name at several places in a page, leading to several rules with maximum score. The heuristic we use to get around this issue consists of adding a new component in the scores of authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node. This new score component takes advantage of the positioning of post's authors which often is a direct child or shares its parent with the post content node.

@@

% Comments
Comments are usually available in separate web feeds, one per blog post. Similarly to blog feeds, comment feeds have a limited number of entries, and in case a blog post has more comments than the ones appearing in the feed, comments have to be extracted from the post web page. To do so we use algorithm \ref{extractionAlgo} with the following modifications:
\begin{enumerate}
  \item Rules that return less HTML nodes than the number of comments on the feed are filtered out.
  \item The score of a rule is the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
\end{enumerate}
Our crawler executes this algorithm on each post that present a comment feed overflow, thus supporting blogs with multiple commenting engines. Comment contents are extracted first, which allows to narrow down the first modification by fixing a target number of comments.

### 2013-11-29 tex/4-techniques.tex
Re-read all the paper, lots of rephrasing.

This section gives an overview of different techniques used in our crawler. We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. The overall software architecture with then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific use case. The section will conclude with a discussion about how the crawler design leads nicely into a scalable and fault resilient distributed architecture.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}
% Introduction
JavaScript is a widely used use language for client-side web scripting. While some applications simply use it for aesthetics aspects such as menus and animations, an increasing number of websites use JavaScript to download and display content. In such circumstances, traditional HTML based crawled would not see the web site as it would be presented to a human visitor and might therefore be obsolete for extracting data from the page.

% Motivation
In our specific use case of crawling the blog sphere, we encountered several blogs where data was missed because of the lack of JavaScript interpretation. The most frequent cases where blogs using the Disqus\cite{disqus2013} and LiveFyre\cite{livefyre2013} comment hosting services. These tools are very handy to setup for webmasters because the entire comments infrastructure is externalized and the setup essential comes down to including a JavaScript snippet in the target web page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time update of comments there are written by users. Less commonly, some blogs are fully rendered using JavaScript. Concretely, when loading such website the web browser will not receive the page content inside an HTML page, but will instead have to execute a script containing the procedure to download and display the page content. On example can be found on the Blogger platforms which proposes as one of its default templates the \emph{Dynamic Views} \cite{antinharasymiv2011} that use this mechanism.

% The solution
To support blogs with JavaScript generated content we embed a full web browser into the crawler. After considering multiple option, we opted for PhantomJS\cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities. In order to take full advantage of all the extraction functionalities, the JavaScript rendering is done as the very first step of blog post processing. This way, every other part of the project is independent of whether or not the page its currently processing was actually rendered by PhantomJS or comes directly from the web server. Extracting blog post content, comments and images therefore works equally well on both blogs with JavaScript generated content and traditional HTML blogs.

% Click click scripting
In addition to extracting page after JavaScript execution, we also use some of PhantomJS scripting capabilities. When the number of comments on one page exceeds a certain threshold, both Disqus and LiveFyre only load a subset of them and end the stream of comments with a \emph{Show More Comments} buttons. As part of the page load process we instruct PhantomJS to repeatedly click on this button until all comments are loaded. As you will see in the evaluation section, \TODO{we will see..}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.47\textwidth]{img/scrapy_architecture.png}
  \caption{Overview of the crawler architecture.}
  \label{architecture}
\end{figure}

Our project is build on top of Scrapy\cite{scrapy2013}, an open source Python framework for web crawling. Scrapy provide an elegant and modulable high-level architecture which we followed in our implementation of the BlogForever Crawler. As illustrated in Figure~\ref{architecture}, Scrapy is divided in several components: \emph{Spiders}, \emph{Item Pipeline}, \emph{Downleader Middlewares} and \emph{Spider Middlewares}, where each of can be used to implement a different functionality.

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog. After downloading the HTML page, blog posts are packed into Items and sent through the folloing pipeline of operation:
\begin{enumerate}[noitemsep]
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download images
  \item Propagate resulting records to the Invenio backend
\end{enumerate}
This pipeline design, often called the \emph{pipes and filters pattern}\cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity. Indeed, disabeling JavaScript rendering or plugging in an alternative backend can be done by editing a single configuration line.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}
% Into, blog-post identification
In order to find and identify blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog-post identification} and \emph{download priority heuristic}. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last in first out} manner. The \emph{blog-post identification} function is able to identify from a URL whether or not the corresponding page is a blog-post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

>>>>

This section gives an overview of different techniques used in our crawler. We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. The overall software architecture with then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific use case. Finally we will talk about deployement to scalable, fault resilient distributed architecture.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}
% Introduction
JavaScript is a widely used use language for client-side web scripting. While some applications simply use it for aesthetics (menus, animations...), an increasing number of websites use JavaScript to download and display content. In such cases, traditional HTML based crawled do not see web pages as they would be presented to a human visitor and might therefore be obsolete for data extraction.

% Motivation
In our experiments crawling the blog sphere, we encountered several blogs where data was missed because of the lack of JavaScript interpretation. The most frequent cases where blogs using the Disqus \cite{disqus2013} and LiveFyre \cite{livefyre2013} comment hosting services. These tools are very handy to setup for web-masters because the entire comments infrastructure is externalized and the setup essential comes down to including a JavaScript snippet in each target page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments. Less commonly, some blogs are fully rendered using JavaScript. When loading such website, the web browser will not receive the page content as an HTML file, but will instead have execute JavaScript code to download and display the page content. One example can be found on the Blogger platforms which provides as one of its default templates the \emph{Dynamic Views} which use this mechanism \cite{antinharasymiv2011}.

% The solution
To support blogs with JavaScript generated content we embed a full web browser into the crawler. After considering multiple option, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities. The JavaScript rendering is done as the very first step of web page processing. Extracting blog post content, comments or images therefore works equally well on both blogs with JavaScript generated content and traditional HTML-only blogs.

% Click click scripting
When the number of comments on one page exceeds a certain threshold, both Disqus and LiveFyre only load a subset of them and end the stream of comments with a \emph{Show More Comments} buttons. As part of the page loading process, we instruct PhantomJS to repeatedly click on these buttons until all comments are loaded. Paths to Disqus and LiveFyre \emph{show more} buttons were manually obtained and are the only non-generic element of the extraction stack which will require human intervention to maintain and extend to other commenting platforms.

@@

\begin{figure}
  \capstart
  \centering
  \includegraphics[width=0.47\textwidth]{img/scrapy_architecture.png}
  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, \cite{scrapy2013})}
  \label{architecture}
\end{figure}

Our crawler is built on top of Scrapy\cite{scrapy2013}, an open source Python framework for web crawling. Scrapy provide an elegant and modulable architecture illustrated in Figure~\ref{architecture}. Several components can be plugged in Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downleader Middlewares} and \emph{Spider Middlewares}; each allowing to implement a different type of functionalities.

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog. After downloading its HTML\TODO{rephrase!}, a web page is packed into an \emph{Item} and sent through the following pipeline of operation:
\begin{enumerate}[noitemsep]
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download images
  \item Propagate resulting records to the Invenio back-end
\end{enumerate}
This pipeline design, often called \emph{pipes and filters pattern} \cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity. Indeed, disabeling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}
% Into, blog-post identification
In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog-post identification} and \emph{download priority heuristic}. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last in first out} manner. The \emph{blog-post identification} function is able to identify from a URL whether or not the corresponding page is a blog-post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

### 2013-11-29 tex/5-evaluation.tex
Re-read all the paper, lots of rephrasing.

Our evaluation will be articulated in two parts. Firstly, we will compare the content extraction procedure presented in section \ref{algorithms} with three open source projects capable of generically extract content from web articles. The comparison will show that our blog targeted solution has better performances both in term of running time and success rates. Secondly, a discussion will be held regarding the different solutions available to archive data beyond what is available in HTML source code. Extraction of authors, dates and comments is not part of the evaluation because of the lack of publicly available competing projects and reference data sets.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction}
The evaluation of post content extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}. Implemented in Javascript, Java and Scala respectively, all three offer the same functionality: given an HTML web page, extract it's main textual content. These projects are more generic than our blog specific approach in the sense that they do not make use of web feeds and do not exploit the fact that pages of a same blog share a similar HTML structure (assuptions \ref{havefeedAssum} and \ref{similarhtmlAssum}). Readability works by .... Boilerpipe uses a very .... Goose implements a more sofisticated algorithm which ....

Table \ref{precisionTable} shows the

Success rates of post content extraction

To evaluate post content extraction
\cite{burton2011} % <- dataset
% intro, plan

% other projects
% \item Boilerpipe https://github.com/misja/python-boilerpipe
% \item Goose https://github.com/grangier/python-goose
% \item Readability https://github.com/buriy/python-readability
% limitation because different approach
Success rates of Content extraction is evaluation

% dataset
% result (table)
\precisionTable
% discussion (15 feed entry)

% running time setup (single core, gc disabled, measure time spent in respective extraction functions)
% result (plot)
\input{runningtimesfigure.tex}

% discussion (c++ vs java vs scala vs go \cite{hundt2011})

>>>>

Our evaluation will be articulated in two parts. Firstly, we will compare the content extraction procedure presented in section \ref{algorithms} with three open source projects capable of generically extract content from web articles. The comparison will show that our blog targeted solution has better performances both in term of running time and success rates. Secondly, a discussion will be held regarding the different solutions available to archive data beyond what is available in HTML source code. Extraction of authors, dates and comments is not part of evaluation because of the lack of publicly available competing projects and reference data sets.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction Precision}
To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}. Implemented in Javascript, Java and Scala respectively, all three offer the same functionality: given an HTML web page, extract it's main textual content. These projects are more generic than our blog specific approach in the sense that they do not make use of web feeds and do not exploit structural similarities of pages of a blog (assuptions \ref{havefeedAssum} and \ref{similarhtmlAssum}). Readability works by .... Boilerpipe uses a very .... Goose implements a more sofisticated algorithm which ....

% dataset
\cite{burton2011}

% table
Table \ref{precisionTable} shows the
\precisionTable

% short discussion, stress the fact that we use different tools

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content running time}

% rsetup (single core, gc disabled, measure time spent in respective extraction functions)
% result (plot)
\input{runningtimesfigure.tex}

% discussion: we are "cheating" on scalability
% discussion: raw perf (15 feed entry)
% discussion: (c++ vs java vs scala vs go \cite{hundt2011})
